A Study of Immersion Factors Using an Augmented Reality Simulation

### 2009-06-24 trunk/Paper/paper.tex
filled in some technical details

\begin{abstract}
It is extremely challenging to run controlled studies comparing multiple augmented reality (AR) systems.  We use an “AR simulation” approach, in which a virtual reality (VR) system is used to simulate multiple AR systems. In order to validate this approach, we carefully replicated a well-known study by Ellis et al. using our simulator, obtaining comparable results.

@@

Augmented Reality systems may be used to simulate x-ray vision \cite{1383060}.  The ability to see through solid objects has applications in fields ranging from engineering and architecture to military or search-and-rescue operations.  Unfortunately, implementing x-ray vision is not a trivial task.  AR systems have cost issules, including those pertaining to level-of-immersion.  For example, what is the ideal augmented field of view (FOV) for a given scenario?  Other issues relate to tracking the objects in the x-ray view.

motivation??

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=3.5in]{annotated_room.png}
	\caption{Overhead view of virtual room (approx. measure).  Participant is stationary in the center of the room, with initial orientation along ``user view'' arrow.  Top-hat's initial position is outside the front doorway, directly in the participant's view.}
\end{figure}

@@

The experiment was written in python using the Vizard environemnt.  Tracking was done using IntersenseTracker
The HMD we used was a Proview HMD with the following attirbutes. ....  Fill this in.
The computer we used was a Dell with the following specs...........  Fill this in

>>>>

\begin{abstract}
%It is extremely challenging to run controlled studies comparing multiple augmented reality (AR) systems.  We use an “AR simulation” approach, in which a virtual reality (VR) system is used to simulate multiple AR systems. In order to validate this approach, we carefully replicated a well-known study by Ellis et al. using our simulator, obtaining comparable results.

@@

Augmented Reality systems may be used to simulate x-ray vision \cite{1383060}.  The ability to see through solid objects has applications in various fields ranging from engineering and architecture to military or search-and-rescue operations.  Unfortunately, implementing x-ray vision is not a trivial task.  AR systems have cost issules, including those pertaining to level-of-immersion.  For example, what is the ideal augmented field of view (FOV) for a given scenario?  Other issues relate to tracking the objects in the x-ray view, such as GPS dropout errors \cite{4079263}, where tracking is temporarily lost.

In this paper, we study the effects of varying augmented FOV along with object-tracking dropouts.  By using an AR simulation built with virtual reality, it is possible to simulate the tracking dropouts, which would otherwise be difficult or impossible to replicate.  The simulation is a tracking task, where the participant is placed inside a virtual room and visually follows a person outside, walking an unpredictable path.  We wish to answer the following questions.  What effect does varying the augmented FOV have on user tracking performance?  What effect do different dropout lengths have on performance?  What are the interactions between these two variables?

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=3.5in]{figures/augmentedroom.png}
	\caption{Overhead view of virtual room (approx. measure).  Participant is stationary in the center of the room, with initial orientation along ``user view'' arrow.  Top-hat's initial position is outside the front doorway, directly in the participant's view.}
\end{figure}

@@

The experiment was written in Python using the Vizard environment.  Tracking was done using InterSense InertiaCube3 orientation tracker which has 180 Hz update rate.  We used a Pro-View 60 head mounted display which displays $640\times480$ video at 60 Hz, and has 36 degrees vertical field of view.  We did not use stereoscopic display.  We ran the experiment on a 2.4 GHz Intel Core 2 machine with 2 Gb of RAM and a NVIDIA GeForce 9800 GX2 graphics card running Windows XP.
